---
title: "Vignette Title"
author:
- name: First Author
  affiliation: First Author's Affiliation
- name: Second Author
  affiliation: Second Author's Affiliation
  email: corresponding@author.com
package: packageName
output:
  BiocStyle::html_document
abstract: |
  Description of your vignette
vignette: |
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Installation

    BiocManager::install('seandavi/RefineBio')

# Load library

```{r}
library(RefineBio)
```


# RefineBio

This package provides the bridge between Bioconductor and the vast, 
homogeneously-processed transcriptomic
data from [refine.bio](https://www.refine.bio).


Cite the refine.bio project as:

> Casey S. Greene, Dongbo Hu, Richard W. W. Jones, Stephanie Liu, David S. Mejia, Rob Patro, Stephen R. Piccolo, Ariel Rodriguez Romero, Hirak Sarkar, Candace L. Savonen, Jaclyn N. Taroni, William E. Vauclain, Deepashree Venkatesh Prasad, Kurt G. Wheeler. refine.bio: a resource of uniformly processed publicly available gene expression datasets. URL: https://www.refine.bio


# Status

This project is undergoing active development and not meant for general use.

# Usage

## Basic search

```{r}
library(RefineBio)
search_results = rb_search_list()
search_results$count
head(search_results$results)
lapply(search_results$facets,head)
```

## Available Organisms

```{r}
orgs = rb_organisms_list()
head(orgs$results)
```

## Available Platforms

```{r}
plats = rb_platforms_list()
head(plats)
dim(plats)
```


# For developers

## The low level API 

```{r}
library(RefineBio)
client = rb_get_client()
ops = rapiclient::get_operations(client)
names(ops)
print(ops$qn_targets_read)
```

## Roadmap

- [x] Basic API endpoints
  - [x] Automated mapping to R objects
  - [ ] s3 classes and methods for R response objects (subclass of list, basically)
- [x] Low-level [rapiclient-based](https://github.com/bergant/rapiclient) client
- [x] R documentation templated from openapi docs
- [x] Response handling for list and data.frame response
- [ ] Token handling to allow downloads
- [ ] File download capability
- [ ] Metadata with file downloads
- [ ] Import of data into R/Biocondutor objects
- [ ] Vignettes
  - [ ] R-based API
  - [ ] rapiclient-based API
  - [ ] common workflows

# Session info {.unnumbered}

```{r sessionInfo, echo=FALSE}
sessionInfo()
```
