---
title: "RefineBio Search"
output: pdf_document
---

```{r setup, include=FALSE}
library(RefineBio)
```

## Performing a basic search

In order to perform a basic search, run the rb_search_list() function with your search terms. This example will be searching with for experiments involving Medulloblastoma.

```{r, include=TRUE, echo=TRUE}
x = rb_search_list(search = "Medulloblastoma")
```

## Performing a filtered search

You can apply filtered searches in the following filter categories:  
    -organism  
    -technology  
    -platform  
    -has_publication

```{r, include=TRUE, echo=TRUE}
x = rb_search_list(search = "Medulloblastoma",
               organism = "HOMO_SAPIENS",
               technology = "rna-seq",
               platform = "IlluminaHiSeq2500")
               # has_publication=TRUE)
```

These categories, excluding "has_publication" can also take multiple values to further the search.

```{r, include=TRUE, echo=TRUE}
x = rb_search_list(search = "Medulloblastoma",
               organism = "HOMO_SAPIENS",
               technology = "rna-seq",
               platform = "IlluminaHiSeq2500")
               # has_publication=TRUE)
```

## Viewing results

You can view your results by accessing the following elements of the data frame.  
The following is an example for accessing elements of the dataset.  
 
Returning number of search hits:

```{r, include=TRUE, echo=TRUE}
x$count
```

Through the use of facets you can further specify your search by previewing the
number of hits you would obtain if you had applied another filter. For this
example, we will look up the number of hits for different platforms.

```{r, include=TRUE, echo=TRUE}
x$facets$platform_accession_codes
```

To access results from the data frame, you can look for the following categories:
    -id
    -title
    -publication_title
    -description
    -technology
    -accession_code
    -alternate_accession_code
    -submitter_institution
    -has_publication
    -publication_doi
    -publication_authors
    -sample_metadata_fields
    -platform_names
    -platform_accession_codes
    -organism_names
    -pubmed_id
    -num_total_samples
    -num_processed_samples
    -num_downloadable_samples
    -source_first_published
    
The following are some examples of result accession.

```{r, include=TRUE, echo=TRUE}
x$results$id
x$results$sample_metadata_fields
x$results$pubmed_id
```

## Viewing specific result

If you would like to see the results for a specific search hit, then you can access the data frame as follows:

```{r, include=TRUE, echo=TRUE}

```
