---
title: "Getting started with the refinebioc package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{refinebioc}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

The `refinebioc` package is a collection of functions that can be used to refine Bioconductor objects. The package is designed to be used in conjunction with the `BiocFileCache` package, which provides a way to cache Bioconductor objects on disk. The `refinebioc` package provides functions to refine these cached objects, such as filtering, normalizing, and transforming data.

# Installation

You can install the `refinebioc` package from Bioconductor using the following code:

```{r}
if (!requireNamespace("BiocManager", quietly = TRUE)) {
  install.packages("BiocManager")
}
BiocManager::install("seandavi/refinebioc")
```

# Usage

## Loading the package

```{r}
library(refinebioc)
```

## Searching for experiments

```{r cache=TRUE}
experiments <- experiment_listing()
```

## Loading an experiment

```{r}
